---
title: "ExomeCoverage"
author: "Stephen Henderson"
date: "7/4/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Coverage

This code was adapted to a 'tidyverse' friendly version from theoriginal ideas on the [Getting Genetics Done Blog](http://www.gettinggeneticsdone.com/2014/03/visualize-coverage-exome-targeted-ngs-bedtools.html)


The bash script `coverage.sh` to produce the initial coverage estimates for each indivdual sample is like so:

```
#!/bin/bash
# usage:  nohup ./coverage.sh &

CAPTURE_REGION="/mnt/store1/hg38/SeqCap_EZ_Exome_v3_hg19Tohg38.sorted.bed"
BEDTOOLS="/home/rmgzshd/bedtools2/bin/bedtools"


for BAM in *.bam
do

	$BEDTOOLS bamtobed -i $BAM | 
	$BEDTOOLS coverage -hist -b - -a $CAPTURE_REGION |
	grep ^all > $BAM.hist.all.txt
done

```

These filesare used to plot cumulative coverage. The greyed out code originally merged and processed the files created by the script above and saved it tot a single simple text file `coverageRegions.tsv`.   There are too too many overall Regions to label or colour code separately here.

```{r coverage, message=FALSE, warning=FALSE}
library(ggplot2)
library(RColorBrewer)
library(tidyverse)


# load and parse the files
#COVERAGE<-list.files(pattern="all.txt$") %>% 
#  sapply(read_tsv, simplify=FALSE, col_names= FALSE) %>%
#  bind_rows(.id = "id") %>%
#  select(id, 3:6) %>%
#  rename(covThreshold = X2, diffFracBelowThreshold = X5) %>%
#  group_by(id) %>%
#  mutate(fracAboveThreshold = 1 - cumsum(diffFracBelowThreshold))

#write_tsv(COVERAGE, "coverageRegions.tsv")
COVERAGE<- read_tsv("coverageRegions.tsv")

# plot the data
maxCov=400
theme_set(theme_bw())
ggplot(subset(COVERAGE, covThreshold < maxCov), aes(x= covThreshold, y=fracAboveThreshold, group=id)) +  geom_line() + ylim(0, 1)

```


